Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box

### 2015-05-06 paper/paper 2/paper 2.tex
THE ROLE OF REASONING FOR RDF VALIDATION

In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
where experts from industry, government, and academia discussed first use cases for RDF constraint\footnote{For simplicity reasons, we use the terms \emph{constraint types/constraints} instead of \emph{RDF constraint types/RDF constraints} in the rest of the paper} formulation and RDF data validation.
In 2014, two working groups on RDF validation have been established to focus on RDF validation: 
the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}. 
Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of RDF validation requirements
which is available for contribution at \url{http://purl.org/net/rdf-validation}.
The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
Bosch et al. identified 74 requirements to formulate constraints; each of them corresponding to a constraint type which can be expressed by at least one existing constraint language \cite{BoschNolleAcarEckert2015}.

>>>>

In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
where experts from industry, government, and academia discussed first use cases for RDF constraint\footnote{For simplicity reasons, we use the terms \emph{constraint types/constraints} instead of \emph{RDF constraint types/RDF constraints} in the remainder of the paper} formulation and RDF data validation.
In 2014, two working groups on RDF validation have been established to focus on RDF validation: 
the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}. 
Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of RDF validation requirements
which is available for contribution at \url{http://purl.org/net/rdf-validation}.
The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
Bosch et al. identified 74 requirements to formulate constraints; each of them corresponding to a constraint type which can be expressed by at least one existing constraint language \cite{BoschNolleAcarEckert2015}.
